---
title: "Exercise week2"
author: "Daniëlle Remmerswaal"
date: "5-10-2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("poLCA") 
library(poLCA)
sessionInfo()
```


# Exercise 

Design a study that:

  a. Does something that requires RNG
  b. Fixes the RNG seed
  c. Replicates the results
  d. Generates an reproducible archive/reprex/markdown
  e. Will run on my machine without trouble (package installs may be excused)
  f. Communicates the info of your session
  
Polca is a package that can be used for Latent Class Analysis of Varibles with polytomous outcomes (multiple categotical outcomes, so not just binary outcomes). 
  
```{r}
set.seed(124)
mysim <- poLCA.simdata(N=5000,nclass=3,ndv = 4, missval = TRUE, pctmiss = .15)
mysim$nresp #randomly generated
mysim$P #proportions in each class
```
created a simulated dataset with 4 categorical questions (with the vector of nresp showing the nr of possible answers each) and one covariant (niv=1). in the simulated data 15% is missing. 

Now we can fit a poLCA model
```{r}
mymodel <- cbind(Y1,Y2,Y3,Y4)~1
class2 <- poLCA(formula=mymodel, data=mysim$dat,nclass=2,na.rm=F,nrep=10)
class3 <- poLCA(formula=mymodel, data=mysim$dat,nclass=3,na.rm=F,nrep=10)
```
```{r}
class2$P
class3$P
```
```{r replicate}
set.seed(124)
mysim <- poLCA.simdata(N=5000,nclass=3,ndv = 4, missval = TRUE, pctmiss = .15)
mysim$nresp #randomly generated
mysim$P #proportions in each class
```



```

